signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-17 paper.tex
addded enccomp figure

\draw [color=red!30!black!50, line width=1.5mm, decorate,decoration={brace,amplitude=20pt,mirror,raise=10pt},yshift=-10pt]
(1,-2.8) -- (12,-2.8) node [branch2, midway, yshift=-1.5cm,color=black] {\textbf{Observations, $\sum_{i=1}^k d_i = T$}};

\end{tikzpicture}
\caption{General scheme of hidden semi-Markov model}
\label{fig:hsmm}
\end{figure}

@@

\begin{table}[ht]
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, E, K, Q, R \\ 
   \rowcolor[gray]{0.85}D, G, N, P, S, T \\ 
  C, H, I, L, M, V \\ 
   \rowcolor[gray]{0.85}F, W, Y \\ 
   \bottomrule
\end{tabular}
\caption{Best-sensitivity (final) encoding} 
\label{tab:best}
\end{minipage}
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, C \\ 
   \rowcolor[gray]{0.85}D, E, H, K, N, Q, R \\ 
  G, P, S, T, Y \\ 
   \rowcolor[gray]{0.85}F, I, L, M, V, W \\ 
   \bottomrule
\end{tabular}
\caption{Best-specificity encoding} 
\label{tab:worst}
\end{minipage}
\end{table}

>>>>

(1,-2.8) -- (12,-2.8) node [branch2, midway, yshift=-1.5cm,color=black] {\textbf{Observations, $\sum_{i=1}^k d_i = T$}};

\end{tikzpicture}
\caption{General scheme of hidden semi-Markov model.}
\label{fig:hsmm}
\end{figure}

@@

\begin{table}[ht]
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
A, E, K, Q, R \\ 
   \rowcolor[gray]{0.85}D, G, N, P, S, T \\ 
  C, H, I, L, M, V \\ 
   \rowcolor[gray]{0.85}F, W, Y \\ 
   \bottomrule
\end{tabular}
\caption{Best-sensitivity (final) encoding.} 
\label{tab:best}
\end{minipage}
\begin{minipage}{.5\linewidth} 
\centering
\begin{tabular}{l}
  \toprule
Groups \\ 
  \midrule
D, E, H, K, N, Q, R \\ 
   \rowcolor[gray]{0.85}G, P, S, T, Y \\ 
  F, I, L, M, V, W \\ 
   \rowcolor[gray]{0.85}A, C \\ 
   \bottomrule
\end{tabular}
\caption{Worst-sensitivity encoding.} 
\label{tab:worst}
\end{minipage}
\end{table}

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/enccomp.png}
\caption{A comparision of encodings.}
\label{fig:enccomp}
\end{figure}
